The Cluster Difference Imaging Photometric Survey (CDIPS). I. Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-06-24 paper/ms.tex
update plots

How
ever, a homogeneous membership calculation for every known
cluster is outside our scope.  So too is a homogeneous search for
young stars across the galaxy.
Instead, we opt to collect
and concatenate appropriate catalogs from across the literature.  
We then use the resulting meta-catalog to identify our target stars within the 
TESS images.

@@

\begin{figure*}[!ht]
	\gridline{\fig{astromresidual_hist.png}{0.5\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{astromresidual_quiver.png}{0.5\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{astromresidual_apertures.png}{0.5\textwidth}{}}
	\caption{
		{\it Top.} Histogram
		{\it Middle.} Vector
		{\it Bottom.} Apertures
	}
	\label{fig:astromresid}
\end{figure*}

@@

The astrometric residual is displayed for one photometric reference
frame (to be described shortly) in
Figure~\ref{fig:astrometricresidual}.
A few salient points can be made.
First, the typical median precision of the WCS solution is a bit below
0.1 pixels, and its $90^{\rm th}$ percentile is typically less than
0.3 pixels\footnote{In fact, in our reduction we automatically impose
that the median residual and 90th percentile remain below 0.2 and 0.4
pixels, respectively.}.
The distribution has a outlier tail of saturated stars which were
masked, and thus do not have measureable centroid positions.
The errors are typically largest in the corners of the field of view,
where the non-linearity of the focal plane is most significant, and
where the corrections required by the SIP coefficients are largest.
The final sub-panel of Figure~\ref{fig:astrometricresidual} is a
sanity check on the location of the projected positions, and also
gives some context for our chosen aperture radii of 1, 1.5, and 2.25
pixels.

>>>>

However, a homogeneous membership calculation for every known
cluster is outside our scope.  So too is a homogeneous search for
young stars across the galaxy.
Instead, we opt to collect
and concatenate appropriate catalogs from across the literature.  
We then use the resulting meta-catalog to identify our target stars within the 
TESS images.

@@

\begin{figure}[!t]
	\gridline{\fig{astromresidual_hist.png}{0.5\textwidth}{}}
	\vspace{-0.8cm}
	\gridline{\fig{astromresidual_quiver.png}{0.5\textwidth}{}}
  %\vspace{-0.8cm}
	%\gridline{\fig{astromresidual_apertures.png}{0.5\textwidth}{}}
	\vspace{-0.8cm}
    \caption{
		{\it Top.} {\bf Histogram of astrometric residual.} The $x$-axis shows 
		the distance between the measured centroid positions of stars, 
		compared to the predicted positions from the WCS solution.
		{\it Bottom.} {\bf Vector plot of astrometric residual.} Each arrow is 
		the vector from the measured to the projected star position. 
		Directions are correct, but lengths are 50 times their true size for 
		visualization purposes.
        The systematic error in the top-right corner is a typical problem in 
        wide-field astrometry.
        The frame chosen for this plot is the photometric reference frame used 
        for Sector 6, Camera 1, CCD 1; we automatically 
        impose cutoffs on the median and $90^{\rm th}$ percentile of the 
        astrometric residual in order to ensure similar levels of astrometric 
        precision are maintained throughout the reduction.
	}
	\label{fig:astromresid}
\end{figure}

@@

The astrometric residual is displayed for one photometric reference
frame (to be described shortly) in
Figure~\ref{fig:astromresid}.
A few salient points can be made.
First, the typical median precision of the WCS solution is a bit below
0.1 pixels, and its $90^{\rm th}$ percentile is typically less than
0.3 pixels\footnote{In fact, in our reduction we automatically impose
that the median residual and 90th percentile remain below 0.2 and 0.4
pixels, respectively.}.
The distribution has a outlier tail of saturated stars which were
masked, and thus do not have measureable centroid positions.
The errors are typically largest in the corners of the field of view,
where the non-linearity of the focal plane is most significant, and
where the corrections required by the SIP coefficients are largest.
The final sub-panel of Figure~\ref{fig:astrometricresidual} is a
sanity check on the location of the projected positions, and also
gives some context for our chosen aperture radii of 1, 1.5, and 2.25
pixels.
